Inequality in socioemotional skills: a cross-cohort comparison

### 2019-09-17 codes/R/paper/seskills_jpube_rev.Rnw
finalise figures and include in manuscript

<<READ, cache=FALSE >>=
library(here)
read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/2b_efa_all.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_no511.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_bootstrap.R"))
read_chunk(here("codes/R/5_selectvars.R"))
read_chunk(here("codes/R/5_sumstats.R"))
read_chunk(here("codes/R/6_graphs.R"))
read_chunk(here("codes/R/6_graphs_ineq.R"))
read_chunk(here("codes/R/6_graphs_item.R"))
read_chunk(here("codes/R/7_ineq_quantiles.R"))
read_chunk(here("codes/R/8_regs_dep.R"))
read_chunk(here("codes/R/8_regs_outc.R"))
read_chunk(here("codes/R/99_auxfun.R"))

@@

@@

>>>>

<<READ, cache=FALSE >>=
library(here)
read_chunk(here("codes/R/1_load.R"))
read_chunk(here("codes/R/2_efa.R"))
read_chunk(here("codes/R/2b_efa_all.R"))
read_chunk(here("codes/R/3_inv_main.R"))
read_chunk(here("codes/R/3_inv_aux.R"))
read_chunk(here("codes/R/3_inv_no511.R"))
read_chunk(here("codes/R/3_inv_fit.R"))
read_chunk(here("codes/R/4_bootstrap.R"))
read_chunk(here("codes/R/5_selectvars.R"))
read_chunk(here("codes/R/5_sumstats.R"))
read_chunk(here("codes/R/6_graphs.R"))
read_chunk(here("codes/R/6_graphs_ineq.R"))
read_chunk(here("codes/R/6_graphs_item.R"))
read_chunk(here("codes/R/7_ineq_quantiles.R"))
read_chunk(here("codes/R/8_regs_dep.R"))
read_chunk(here("codes/R/8_regs_outc.R"))
read_chunk(here("codes/R/9_rif.R"))
read_chunk(here("codes/R/99_auxfun.R"))

@@

<<RIF_PLOTS_PREP, dependson="SELECTDATA">>=
# make RIF decomposition plots
@

@@

\begin{figure}
<<RIF_PLOTS, dependson="RIF_PLOTS_PREP", dev='tikz', fig.height=8, fig.width=10, out.width='\\linewidth'>>=
gridExtra::grid.arrange(rif_plots[[1]],rif_plots[[2]], ncol=1, nrow=2)
@
\caption{RIF decomposition of quantile differences}\label{fig:rif}
\justify {\scriptsize \emph{Notes}: 
\par}
\end{figure}
